Brief notes on erosion

### 2019-04-22 docs/proposals/ErosionWhitePaper.tex
fixed small typo in white paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved Numerical Methods}
\begin{wrapfigure}[22]{r}{0.4\textwidth}
\centering
\input{figs/vort1.tikz}
\caption{\label{fig:vort1} \em The vorticity along a vertical slice
cutting through a single body.  There are solid walls at $y = \pm 1$,
and an eroding body at $y = (-0.5,0.5)$.  The trapezoid rule gives large
errors near the solid walls, while the Barycentric quadrature formula
results in a smooth vorticity field.}
\end{wrapfigure}

Our current formulation fixes all bodies space.  However, in reality,
the bodies are also transported by the flow.  The PI has simulated
moving interfaces in Stokes flow~\cite{qua-bir2015b, qua-bir2014,
qua-bir2016}. More recently, the PI and his former Ph.D.~student
developed time stepping methods for rigid body transport in Stokes
flow~\cite{bys-sha-qua2018}.  This work extends a contact algorithm,
originally developed by Lu et al.~\cite{lu-rah-zor2017}, to accuratly
simulate the dynamics of nearly-touching rigid bodies.  The contact
algorithm resolves errors introduced by time stepping, but quadrature
error introduced by the BIE formulation must also be addressed.  A
postdoc in the PI's group is extending a Barycentric near-singular
integration scheme developed by Barnett et al.~\cite{bar-wu-vee2015} to
develop quadrature formula to accurately compute the shear stress,
vorticity, and other physical quantities.  In Figure~\ref{fig:vort1},
the vorticity is computed along a vertical slice that cuts through a
single eroding body.  The trapezoid rule is accurate far from the solid
walls ($y = \pm 1$) and the boundary of the eroding body ($y = \pm
0.5$), but introduces large errors near the walls and body.  However,
our new Barycentric quadrature rule is uniformly accurate throughout the
entire fluid domain.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Improved Numerical Methods}
\begin{wrapfigure}[22]{r}{0.4\textwidth}
\centering
\input{figs/vort1.tikz}
\caption{\label{fig:vort1} \em The vorticity along a vertical slice
cutting through a single body.  There are solid walls at $y = \pm 1$,
and an eroding body at $y = [-0.3,0.5]$.  The trapezoid rule gives large
errors near the solid walls, while the Barycentric quadrature formula
results in a smooth vorticity field.}
\end{wrapfigure}

Our current formulation fixes all bodies space.  However, in reality,
the bodies are also transported by the flow.  The PI has simulated
moving interfaces in Stokes flow~\cite{qua-bir2015b, qua-bir2014,
qua-bir2016}. More recently, the PI and his former Ph.D.~student
developed time stepping methods for rigid body transport in Stokes
flow~\cite{bys-sha-qua2018}.  This work extends a contact algorithm,
originally developed by Lu et al.~\cite{lu-rah-zor2017}, to accuratly
simulate the dynamics of nearly-touching rigid bodies.  The contact
algorithm resolves errors introduced by time stepping, but quadrature
error introduced by the BIE formulation must also be addressed.  A
postdoc in the PI's group is extending a Barycentric near-singular
integration scheme developed by Barnett et al.~\cite{bar-wu-vee2015} to
develop quadrature formula to accurately compute the shear stress,
vorticity, and other physical quantities.  In Figure~\ref{fig:vort1},
the vorticity is computed along a vertical slice that cuts through a
single eroding body.  The trapezoid rule is accurate far from the solid
walls ($y = \pm 1$) and the boundary of the eroding body ($y \in
[-0.3,0.5]$), but introduces large errors near the walls and body.
However, our new Barycentric quadrature rule is uniformly accurate
throughout the entire fluid domain.
